Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks

### 2018-11-14 paper_prd.tex
work on the draft

@@

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
\hspace{-0.cm}
\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
\hspace{-0.cm}
\\
\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
\hspace{-0.cm}
\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
\hspace{-0.cm}
\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disks. In the first row, we show this for all of our KBHsSH models. In the second row, we show this for a sequence of Kerr BHs with increasing spin parameter. \tf{Using yellow is a bad choice as it cannot be seen, especially on print. Please change the colour of the yellow dots to some other colour or symbol.}}
\label{comparison_HBH_Kerr_dens_enth}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.4\textwidth]{figures/fig8_HBH.eps}
\hspace{0.5cm}
\includegraphics[width=0.4\textwidth]{figures/fig8_Kerr.eps}
\hspace{0.5cm}
\caption{Effects of the magnetization on the perimeteral location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre), $R_{\mathrm{mag}, \mathrm{max}} - R_{\mathrm{c}})/ R_{\mathrm{c}}$). Left panel: KBHsSH models. Right panel: A sequence of KBHs with increasing spin parameter. \tf{Change the $r$ to $R$ in the vertical labels.}}
\label{comparison_HBH_Kerr_r_m_max}
\end{figure*}

\begin{table*}[t]
\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}        
\label{KBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c  c c c c c c c}
\hline\hline       
 $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.00$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
 \hline 
 $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.00$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
\hline  
$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.00$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
 \hline 
$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.29$ & $1.51$ & $1.10 \times 10^{-1}$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.00$ & $6.17$ & $1.22 \times 10^{-10}$ & $4.91 \times 10^{-1}$ & $2.0021$ & $2.0030$ \\ 
\hline   
\end{tabular}
\end{table*}

\begin{table}
\caption{Angular velocity at the centre for the different models computed. In the first column, we present the angular velocity at the disc centre for the different KBHsSH models. In the second column, we present the angular velocity at the disc centre for a KBH with the same ADM quantities.\sg{to fill with the Kerr case values.}}
\label{angular_velocity_table}      
\centering          
\begin{tabular}{c c c }
\hline\hline       
 Model & $\Omega_{\mathrm{c}}$ & $\Omega_{\mathrm{ADM_c}}$ \\ 
\hline           
I & $0.493$ & $-$ \\ 
 \hline 
II & $0.424$ & $--$ \\
 \hline 
III & $0.521$ & $-$ \\ 
 \hline 
IV & $0.427$ & $-$ \\ 
 \hline 
V & $0.394$ & $-$ \\ 
 \hline 
VI & $0.350$ & $-$ \\ 
 \hline 
VII & $0.330$ & $-$ \\ 
\hline      
\end{tabular}
\end{table}

\begin{table}
\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$. In the first column, we present the value of the central density for the different KBHsSH models. In the second column, we present the central density for a KBH with the same ADM quantities.\sg{To fill with the Kerr case values.}}
\label{central_density_table}      
\centering          
\begin{tabular}{c c c c }
\hline\hline       
 Model & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{ADM_c}}$ \\ 
\hline           
I & $10^{10}$ & $0.002051$ & $-$ \\ 
 \hline 
 & $1$ & $0.00434$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.00531$ & $-$ \\ 
 \hline 
II & $10^{10}$ & $0.00150$ & $-$ \\ 
 \hline 
 & $1$ & $0.00427$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.00582$ & $-$ \\ 
 \hline 
III & $10^{10}$ & $0.00304$ & $-$ \\ 
 \hline 
 & $1$ & $0.00840$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.0108$ & $-$ \\ 
 \hline 
IV & $10^{10}$ & $0.00407$ & $-$ \\ 
 \hline 
 & $1$ & $0.00897$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.0110$ & $-$ \\ 
 \hline 
V & $10^{10}$ & $0.00577$ & $-$ \\ 
 \hline 
 & $1$ & $0.0104$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.0121$ & $-$ \\ 
 \hline 
VI & $10^{10}$ & $0.00762$ & $-$ \\ 
 \hline 
 & $1$ & $0.0116$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.0131$ & $-$ \\ 
 \hline 
VII & $10^{10}$ & $0.0129$ & $-$ \\ 
 \hline 
 & $1$ & $0.0162$ & $-$ \\ 
 \hline 
 & $10^{-10}$ & $0.01701$ & $-$ \\ 
 \hline     
\end{tabular}
\end{table}

@@

For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$. Our numerical approach can handle BH spins as large as $|a-1|=10^{-10}$ \tf{Check} but such extreme cases do not add further relevant information to our discussion. Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}. As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$. It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$. \tf{Describe further the table and the figures}. \tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.}

@@

\sg{Compare the radial profiles.}
\sg{Describe and compare the angular velocity at the centre.}

@@

The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}. The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to our sequence of Kerr BHs with increasing spin parameter. For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetisation) and also higher values for $\rho_{\mathrm{max}}$ (high magnetisation). However, there are quantitative differences between the two cases. For the enthalpy, the values of $h_{\mathrm{max}}$ reached for disks around KBHsSH are much higher than those of the Kerr BH case. This implies that, while the $w = \rho h \simeq \rho$ approximation (employed in~\cite{Komissarov:2006,Gimeno-Soler:2017}) is valid for magnetized disks ($\beta_{\mathrm{m_c}} \sim 1$) around Kerr BHs for values of the spin parameter as high as $a \sim 0.99$, that is not the case for disks around KBHsSH. We note that for the most extreme spin value we can build, $a=XXX$, the maximum enthalpy is $h_{\rm max}=XXX$. \tf{Complete.}
%Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).

>>>>

\begin{figure*}
\centering
\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
\hspace{-0.6cm}
\caption{Size of the disks. Effects of the magnetisation on the radial profiles of the logarithm of the density at the equatorial plane for different KBH models. From left to right we show three different cases with the same ADM quantities as the KBHsSH model I, IV, and VII, respectively.}
\label{radial_profiles_KBH}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
\hspace{-0.cm}
\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
\hspace{-0.cm}
\\
\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
\hspace{-0.cm}
\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
\hspace{-0.cm}
\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disks. In the first row, we show this for all of our KBHsSH models. In the second row, we show this for a sequence of Kerr BHs with increasing spin parameter. \tf{Using yellow is a bad choice as it cannot be seen, especially on print. Please change the colour of the yellow dots to some other colour or symbol.}\sg{I increased the size of the dots a and added a black edge.}}
\label{comparison_HBH_Kerr_dens_enth}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.4\textwidth]{figures/fig8_HBH.eps}
\hspace{0.5cm}
\includegraphics[width=0.4\textwidth]{figures/fig8_Kerr.eps}
\hspace{0.5cm}
\caption{Effects of the magnetization on the perimeteral location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre), $R_{\mathrm{mag}, \mathrm{max}} - R_{\mathrm{c}})/ R_{\mathrm{c}}$). Left panel: KBHsSH models. Right panel: A sequence of KBHs with increasing spin parameter. \tf{Change the $r$ to $R$ in the vertical labels.} \sg{Done}}
\label{comparison_HBH_Kerr_r_m_max}
\end{figure*}

\begin{table*}[t]
\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}        
\label{KBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c c  c c c c c c c}
\hline\hline       
 $a$ & $\mathfrak{s}$ &  $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
$0$ & & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
 \hline 
 &  &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
 \hline 
 &  &  & &  &  & $10^{-10}$ & $1.00$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
 \hline 
 $0.5$ & & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
 \hline 
 &  &  & &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
 \hline  
 &  &  & &  &  & $10^{-10}$ & $1.00$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
\hline  
$0.9$ &  & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
 \hline 
 &  &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
 \hline 
 &  &  &  &  &  & $10^{-10}$ & $1.00$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
 \hline 
$0.9999$ &  & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
\hline 
 &  &  &  &  &  & $1$ & $1.29$ & $1.51$ & $1.10 \times 10^{-1}$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
\hline 
 &  &  &  &  &  & $10^{-10}$ & $1.00$ & $6.17$ & $1.22 \times 10^{-10}$ & $4.91 \times 10^{-1}$ & $2.0021$ & $2.0030$ \\ 
\hline   
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$. In the first column, we present the value of the central density for the different KBHsSH models. In the second column, we present the central density for a KBH with the same ADM quantities.\sg{To fill with the Kerr case values.}}
\label{central_density_table}      
\centering          
\begin{tabular}{c c c c c c c c c}
\hline\hline       
 Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}} (\mathrm{g} \dot cm^{-3})$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}(\mathrm{g} \dot cm^{-3})$ & $\mathfrak{s}_{\mathrm{ADM}}$ \\ 
\hline           
I & $0.493$ & $10^{10}$ & $6.818 \times 10^{-4}$ & & $0.854$ & $3.752 \times 10^{-3}$ &   & $1.589$ \\ 
 \hline 
 & & $1$ & $2.185 \times 10^{-3}$ & & & $7.942 \times 10^{-3}$ & & \\ 
 \hline 
 & & $10^{-10}$ & $3.227 \times 10^{-3}$ & & & $7.641 \times 10^{-3}$ & & \\ 
 \hline 
II & $0.424$ & $10^{10}$ & $3.216 \times 10^{-4}$ & & $-$ & $-$ & & $-$ \\ 
 \hline 
 & & $1$ & $1.651 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
 & & $10^{-10}$ & $3.026 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
III & $0.521$ & $10^{10}$ & $8.120 \times 10^{-4}$ & & $0.163$ & $-$ & & $1.278$ \\ 
 \hline 
 & & $1$ & $3.497 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
 & & $10^{-10}$ & $5.452 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
IV & $0.427$ & $10^{10}$ & $1.197 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
 \hline 
 & & $1$ & $3.421 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
 & & $10^{-10}$ & $5.135 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
V & $0.394$ & $10^{10}$ & $1.792 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
 \hline 
 & & $1$ & $3.883 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
 & & $10^{-10}$ & $5.435 \times 10^{-3} $ & & & $-$ & & \\ 
 \hline 
VI & $0.350$ & $10^{10}$ & $2.348 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
 \hline 
 & & $1$ & $4.106 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
 & & $10^{-10}$ & $5.685 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
VII & $0.330$ & $10^{10}$ & $3.737 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
 \hline 
 & & $1$ & $5.356 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline 
 & & $10^{-10}$ & $7.598 \times 10^{-3}$ & & & $-$ & & \\ 
 \hline     
\end{tabular}
\end{table*}

@@

For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$. Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ \sg{Done}\tf{Check} but such extreme cases do not add further relevant information to our discussion. Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}. As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$. It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$. \tf{Describe further the table and the figures}. \tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.}

@@

In Fig~\ref{radial_profiles_KBH}, we show three KBH models with the same ADM mass and angular momentum as the cases shown in Fig.~\ref{radial_profiles_HBH}. The first case corresponds to a near-extremal KBH ($a = 0.9987$) and the other two have a similar value for spin parameter ($0.8489$ and $0.8941$ respectively). Direct comparison between this models and the KBHsSH ones, draws out very interesting features of these models. It can be seen that, for model I, the disc in the Kerr case is considerably smaller than its hairy counterpart...

\sg{Describe and compare the angular velocity at the centre.}

@@

The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}. The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to our sequence of Kerr BHs with increasing spin parameter. For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetisation) and also higher values for $\rho_{\mathrm{max}}$ (high magnetisation). However, there are quantitative differences between the two cases. For the enthalpy, the values of $h_{\mathrm{max}}$ reached for disks around KBHsSH are much higher than those of the Kerr BH case. This implies that, while the $w = \rho h \simeq \rho$ approximation (employed in~\cite{Komissarov:2006,Gimeno-Soler:2017}) is valid for magnetized disks ($\beta_{\mathrm{m_c}} \sim 1$) around Kerr BHs for values of the spin parameter as high as $a \sim 0.99$, that is not the case for disks around KBHsSH. We note that for the most extreme spin value we can build, $a=0.9999999$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$. \tf{Complete.} \sg{Done}
%Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
